Verifying Spatial Properties of Array Computations

### 2017-04-15 oopsla17/study.tex

\begin{tabular}{lS[table-format=4]S[table-format=2.2]S[table-format=2.2]lS[table-format=4]S[table-format=2.2]S[table-format=2.2]}

@@

                                              & \% {(of group)}
&\textbf{Position} & \textbf{Number} & \% {(whole)} & \% {(group)} \\ \hline

@@

& 31 & 0.03\% & 0.03\% \\ \hline

@@

 & 0.00\% & 0.00\% \\ \hline

@@

& & \textsf{away} & 152 & 0.14\% & 0.17 \% \\
& 83689 & 76.94\% & 94.48\% & \textsf{origin} & 81309 & 74.75\% & 91.79\% \\
&&&& \textsf{straddle} & 2228 & 2.05\% & 2.52\% \\ \hline

@@

 & 4.46\% & 5.48\%  \\ \hline \hline

@@

Thus, $76.94\%$ of array computations have only contiguous
neighbour indices (which may include constants in some indices)
in a contiguous pattern on the right hand side, with $76.80\%$
either at the origin ($74.75\%$) or offset by a distance of 1 from the origin

@@

were found of index patterns not immediate next to or over the origin.

>>>>

\begin{tabular}{lS[table-format=4]S[table-format=2.2]lS[table-format=4]S[table-format=2.2]}

@@

&\textbf{Position} & \textbf{Number} & \% {(of whole)} \\ \hline

@@

& 31 & 0.03\% \\ \hline

@@

 & 0.00\% & \\ \hline

@@

 & \textsf{away} & 152 & 0.14\% \\
& 83689 & 76.94\% & \textsf{origin} & 81309 & 74.75\% \\
&&& \textsf{straddle} & 2228 & 2.05\% \\ \hline

@@

 & 4.46\% \\ \hline
Other & 20196 & 18.57\%  \\
 \hline

@@

Thus, $76.94\%$ of array computations have only contiguous neighbour
indices (which may include constants in some indices) in a contiguous
pattern on the right hand side, with $76.80\%$ either at the origin
($74.75\%$) or offset by a distance of 1 from the origin

@@

of index patterns not immediately next to or over the origin were
found.  There is a non trivial amount of non-contiguous arrays access,
but it is a much smaller proportion of the whole.

\begin{enumerate}[resume]
\item Many array computations are \emph{stencil computations}:
an assignment whose
 right-hand side comprises array subscripts with neighbourhood indices
and whose left-hand side is an neighbourhood-indexed array subscript
(\eg{}, the classic five-point stencil);
\end{enumerate}
